---
title: "compile_jive_results"
author: "Amrit Singh"
date: '2017-12-22'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

WhereAmI <- "~/Dropbox/Manuscript/diablo_datasets/benchmarking/"

## load libraries
library(r.jive)
library(tidyverse)

## load data
load(paste0(WhereAmI, "SNFdatasets.RDATA"))

```

# JIVE

## Colon
Estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 5 , individual ranks: 20 12 11 
JIVE algorithm converged after  485  iterations.
Re-estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 5 , individual ranks: 25 17 20 
JIVE algorithm converged after  194  iterations.
Re-estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 5 , individual ranks: 25 18 19 
JIVE algorithm converged after  162  iterations.
Re-estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 5 , individual ranks: 25 18 20 
JIVE algorithm converged after  265  iterations.
Re-estimating  joint and individual ranks via permutation...
Final joint rank: 5 , final individual ranks: 25 18 20 
    user   system  elapsed 
3399.332  109.718 3516.703

```{r}
system.time(jive_colon <- jive(lapply(snf_data$colon, t)))
saveRDS(jive_colon, paste0(WhereAmI, "jive/jive_colon.rds"))
jive_colon <- readRDS(paste0(WhereAmI, "jive/jive_colon.rds"))
```

## Kidney
Estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 8 , individual ranks: 22 14 21 
JIVE algorithm converged after  265  iterations.
Re-estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 8 , individual ranks: 26 22 33 
JIVE algorithm converged after  246  iterations.
Re-estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 8 , individual ranks: 26 21 33 
JIVE algorithm converged after  381  iterations.
Re-estimating  joint and individual ranks via permutation...
Final joint rank: 8 , final individual ranks: 26 21 33 
    user   system  elapsed 
3133.940  116.240 3256.706

```{r}
system.time(jive_kidney <- jive(lapply(snf_data$kidney, t)))
saveRDS(jive_kidney, paste0(WhereAmI, "jive/jive_kidney.rds"))
jive_kidney <- readRDS(paste0(WhereAmI, "jive/jive_kidney.rds"))
```

## GBM
Estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 7 , individual ranks: 23 18 16 
JIVE algorithm converged after  430  iterations.
Re-estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 7 , individual ranks: 25 22 29 
JIVE algorithm did not converge after  1000  iterations.
Re-estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 7 , individual ranks: 25 23 30 
JIVE algorithm did not converge after  1000  iterations.
Re-estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 7 , individual ranks: 25 23 29 
JIVE algorithm did not converge after  1000  iterations.
Re-estimating  joint and individual ranks via permutation...
Final joint rank: 7 , final individual ranks: 25 23 29 
    user   system  elapsed 
9412.532  120.756 9535.102 

```{r}
system.time(jive_gbm <- jive(lapply(snf_data$gbm, t)))
saveRDS(jive_gbm, paste0(WhereAmI, "jive/jive_gbm.rds"))
jive_gbm <- readRDS(paste0(WhereAmI, "jive/jive_gbm.rds"))
```

## Lung
Estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 4 , individual ranks: 23 15 13 
JIVE algorithm converged after  117  iterations.
Re-estimating  joint and individual ranks via permutation...
Running JIVE algorithm for ranks:
joint rank: 4 , individual ranks: 27 22 25 
JIVE algorithm converged after  127  iterations.
Re-estimating  joint and individual ranks via permutation...
Final joint rank: 4 , final individual ranks: 27 22 25 
    user   system  elapsed 
 946.377   56.279 1003.182
 
```{r}
system.time(jive_lung <- jive(lapply(snf_data$lung, t)))
saveRDS(jive_lung, paste0(WhereAmI, "jive/jive_lung.rds"))
jive_lung <- readRDS(paste0(WhereAmI, "jive/jive_lung.rds"))
```

# save objects to RDATA file

```{r}
save(jive_colon=jive_colon, jive_kidney=jive_kidney, jive_gbm=jive_gbm, jive_lung=jive_lung,
  file = paste0(WhereAmI, "jive/jive_SNFdatasets.RDATA"))
```

